---
html_document:
  df_print: paged
date: "20 February 2024"
output:
  # pdf_document:
  #   fig_caption: yes
  #   keep_tex: yes
  html_document:
    df_print: paged
    fig_caption: yes
    toc: true
    toc_float: true
    number_sections: false
fontfamily: mathpazo
fontsize: 11pt
geometry: margin=1in
header-includes: 
  - \linespread{1.05}
  - \usepackage{graphicx}
  - \usepackage{float}
title: "Data Science Week 7 Guided Seminar Script"
classroom: '*online*'
classhours: TBA
web: MOODLE
instructor: Kevin Fahey
email: kevin.fahey@nottingham.ac.uk
officehours: TBD
linkcolor: dullmagenta
citecolor: Maroon
filecolor: red
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.path="figure/graphics-", 
                      cache.path="cache/graphics-", 
                      fig.align="center",
                      external=TRUE,
                      warning=FALSE,
                      fig.pos="H",
                      number_sections = FALSE)

```

# Overview

Today we will be engaging in a very straightforward exercise, with a **substantial** number of opportunities to overlook crucial instructions. Therefore, please read through every component of this document before undertaking any coding.

\
\
\

## Today's packages

You will not need any new packages today. Most of the new coding changes will be in installing GitHub and setting up 'cloning' in RStudio, rather than making major coding changes in R. We will not load in any datasets, instead making some data out of whole cloth and 'pushing' it to GitHub.

```{r preamble, message = F, warning = F}
library(tidyverse)
```

\
\
\

## Setting up your GitHub Account

You will need to set up a GitHub account. You will need to do two things: (1) sign up to GitHub at `https://github.com` with an account, and (2) install Github. We will walk through each of these in turn:

  -- (1) Go to [Github](https://github.com/)

\
\
\

# Walking through GitHub


# Practice Makes Permanent


## Produce a Dataset

```{r make_data, message = F, warning = F}
quant_data <- rnorm(10, 0, 1)
qual_data <- c("Of", "All", "The", "Souls", "I", "Have", "Encountered", "In", "My", "Travels")

df <- tibble::as_tibble(cbind(quant_data, qual_data)) %>%
  mutate(quant_data = as.numeric(paste0(quant_data, sep = "")))

glimpse(df)
```

## Commit and Push to GitHub


# Next Week

Next week we will be working with `ggplot2`, `wordcloud2`, and other visualisation commands to make 